A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
Standardized the temperature usage. I'll submit this one as the first draft to NIPS

We next use logistic regression for the binary classification of 1s versus 7s in the MNIST
dataset~\cite{lecun-mnisthandwrittendigit-2010}. The data has 12007 and 1000 training and testing
points, respectively (we used a random subset of the test data). The propose is again a random walk
with covariance matrix $0.1I$ for the $784\times 784$ identity matrix $I$. We initialize the
posterior temperature at $T_0=3000$, and decrease it according to $T_i = T_0 /\sqrt{i + 1}$ for
iteration $i \ge 1$. We set the minibatch size $m=50$ and compare our minibatch MH test with the
adaptive minibatch.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp2.png}
    \caption{Logistic regression performance (accuracy/log likelihood) and minibatch size analysis.}
    \label{fig:logistic_fig}
    %\vspace{-10pt}
\end{figure}

@@

For our minibatch MH test, in order to enforce the ${\rm std}(\Delta') < 1.2$ condition, we
initialize the temperature $T_0 = 3000$, and decrease it by the rule $T_i =  T_0 /(i + 1)^{3} \mbox{
for } i \leq N/2 \mbox{ and } = T_0 /(i + 1)^{0.2} \mbox{ for } i >N/2 $, where $N=4000$ is
the total number of iterations. If our estimated ${\rm std}(\Delta') \ge 1.2$, we ignore the
current iteration. Figure~\ref{fig:appendixExp2} plots our estimated ${\rm std}(\Delta')$ values
versus iteration count.

>>>>

We next use logistic regression for the binary classification of 1s versus 7s in the MNIST
dataset~\cite{lecun-mnisthandwrittendigit-2010}. The data has 12007 and 1000 training and testing
points, respectively (we used a random subset of the test data). The propose is again a random walk
with covariance matrix $0.1I$ for the $784\times 784$ identity matrix $I$. We initialize the
posterior temperature at $T_0=3000$, and decrease it according to $T_i = T_0 /(i + 1)^{3}$ for $i
\leq N/2$ and $T_i = T_0 /(i + 1)^{0.2}$ for $i >N/2$, where $N=4000$ is the total number of
iterations. We set the minibatch size $m=50$ and compare with adaptive sampling.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp2.png}
    \caption{Logistic regression performance (accuracy/log likelihood) and minibatch size analysis.}
    \label{fig:logistic_fig}
    \vspace{-10pt}
\end{figure}

@@

For our minibatch MH test, in order to enforce the ${\rm std}(\Delta') < 1.2$ condition, we
initialize the temperature $T_0 = 3000$, and decrease it by the rule $T_i = T_0 /(i + 1)^{3}$ for $i
\leq N/2$ and $T_i = T_0 /(i + 1)^{0.2}$ for $i >N/2$, where $N=4000$ is the total number of
iterations. If our estimated ${\rm std}(\Delta') \ge 1.2$, we ignore the current iteration.
Figure~\ref{fig:appendixExp2} plots our estimated ${\rm std}(\Delta')$ values versus iteration
count.
